What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-01 paper/main.tex
add link to formulas

\section{Playing it out} %KYR: may swap order with the next section on artifact availability?

@@

KYR: link LTL database here too.

>>>>

\section{Playing it out} \label{sec:playing}%KYR: may swap order with the next section on artifact availability?

@@

The set of \ltl\ formulas we used to evaluate our tool in \cref{sec:playing} can be found \href{https://github.com/EULIR/ltl-explainability/tree/main/ltl-formulas}{here}.
